Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations

### 2021-11-23 analysis/paper/paper.Rmd
all bioenergetics plots added

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)
```

@@

```{r shoup-temp-data}
temp_df = read_tsv(here("analysis/data/raw_data/USGS_13307000_Salmon_River_Nr_Shoup.txt"),
                   comment = "#") %>%
  rename(discharge_cfs = `47768_00060`,
         discharge_cfs_cd = `47768_00060_cd`,
         gage_ht_ft = `47769_00065`,
         gage_ht_ft_cd = `47769_00065_cd`,
         water_temp_c = `47773_00010`,
         water_temp_c_cd = `47773_00010_cd`)

@@

```{r abund-est}
all_est = LP_mod %>%
  select(event_name, species, model, N:Uci) %>%
  bind_rows(N_mods %>%
             select(event_name, species, model, N:Uci)) %>%
  mutate(range = Uci - Lci,
         prop_range = range / N) %>%
  mutate(across(event_name,
                ~ str_replace(., "_", " "))) %>%
  mutate(model = fct_recode(model,
                            "Schumacher-Eschmeyer" = "SchumacherEschmeyer")) %>%
  arrange(event_name, model)
```

@@

@@

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

@@

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```

>>>>

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)

@@

```{r shoup-temp-data}
shoup_temp_df = read_tsv(here("analysis/data/raw_data/USGS_13307000_Salmon_River_Nr_Shoup.txt"),
                   comment = "#") %>%
  rename(discharge_cfs = `47768_00060`,
         discharge_cfs_cd = `47768_00060_cd`,
         gage_ht_ft = `47769_00065`,
         gage_ht_ft_cd = `47769_00065_cd`,
         water_temp_c = `47773_00010`,
         water_temp_c_cd = `47773_00010_cd`)

```{r read-bio-outputs}
# full year, no growth
full_yr_no_growth = read_csv(here("analysis/data/raw_data/2020 Bioenergetics 1 year.csv")) %>%
  clean_names() %>%
  mutate(date = as.Date(date, format = "%m/%d/%y")) %>%
  mutate(cum_cons_fish_g = cumsum(cons_fish_g)) %>%
  mutate(month = month(date))

# full year, 10% growth
full_yr_10p_growth = read_csv(here("analysis/data/raw_data/2020 Bioenergetics 1 year 10% growth.csv")) %>%
  clean_names() %>%
  mutate(date = as.Date(date, format = "%m/%d/%y")) %>%
  mutate(cum_cons_fish_g = cumsum(cons_fish_g)) %>%
  mutate(month = month(date))

# an alternative model
alternative_mod = read_csv(here("analysis/data/raw_data/Bioenergetics 32 fish 68 inverts.csv")) %>%
  clean_names() %>%
  mutate(date = as.Date(date, format = "%m/%d/%y")) %>%
  mutate(cum_cons_fish_g = cumsum(cons_fish_g)) %>%
  mutate(month = month(date))

# Fall emigration period (9/1 - 11/17), no growth
fall_only_no_growth = read_csv(here("analysis/data/raw_data/78_day_bioenergetics.csv")) %>%
  clean_names() %>%
  mutate(date = as.Date(date, format = "%m/%d/%y")) %>%
  mutate(cum_cons_fish_g = cumsum(cons_fish_g)) %>%
  mutate(month = month(date))

@@

```{r abund-est}
all_est = LP_mod %>%
  select(event_name, species, model, N:Uci) %>%
  bind_rows(N_mods %>%
             select(event_name, species, model, N:Uci)) %>%
  mutate(range = Uci - Lci,
         prop_range = range / N) %>%
  mutate(across(event_name,
                ~ str_replace(., "_", " "))) %>%
  mutate(model = fct_recode(model,
                            "Schumacher-Eschmeyer" = "SchumacherEschmeyer")) %>%
  arrange(event_name, model)

@@

```{r fall-bio-fig, fig.cap = "First bioenergetics plot."}
fall_bio_p = fall_only_no_growth %>%
  ggplot() +
  aes(x = date,
      y = cum_cons_fish_g,
      colour = temperature_c) +
  geom_line(size = 2.5) +
  scale_color_distiller(palette = "Spectral",
                        direction = -1) +
  scale_x_date(breaks = "2 week") +
  scale_y_continuous(name = "Scumulative fish eaten (g)",
                     breaks = seq(0, 200, by = 10),
                     sec.axis = sec_axis(~. / 12, 
                                         name = "Potential number of Chinook Salmon smolts",
                                         breaks = seq(0, 20, by = 1))) +
  theme_classic() +
  theme(legend.position = "top") +
  labs(color = "Temperature (C)")

fall_bio_p

```{r full-yr-ng-fig, fig.cap = "Next bioenergetics plot."}
full_yr_ng_p = full_yr_no_growth %>%
  ggplot() +
  aes(x = date,
      y = cum_cons_fish_g,
      colour = temperature_c) +
  geom_line(size = 2.5) +
  scale_color_distiller(palette = "Spectral",
                        direction = -1) +
  #scale_x_date(breaks = "2 week") +
  scale_y_continuous(name = "Cumulative fish eaten (g)",
                     breaks = seq(0, 600, by = 50),
                     sec.axis = sec_axis(~. / 12,
                                         name = "Potential number of Chinook Salmon smolts",
                                         breaks = seq(0, 30, by = 2))) +
  theme_classic() +
  theme(legend.position = "top") +
  labs(color = "Temperature (C)",
       x = "Month")

full_yr_ng_p

```{r full-yr-10p-fig, eval = F, fig.cap = "Another bioenergetics plot."}
full_yr_10p_p = full_yr_10p_growth %>%
  ggplot() +
  aes(x = date,
      y = cum_cons_fish_g,
      colour = temperature_c) +
  geom_line(size = 2.5) +
  scale_color_distiller(palette = "Spectral",
                        direction = -1) +
  #scale_x_date(breaks = "2 week") +
  scale_y_continuous(name = "Cumulative fish eaten (g)",
                     breaks = seq(0, 600, by = 50),
                     sec.axis = sec_axis(~. / 12,
                                         name = "Potential number of Chinook Salmon smolts",
                                         breaks = seq(0, 40, by = 2))) +
  theme_classic() +
  theme(legend.position = "top") +
  labs(color = "Temperature (C)",
       x = "Month")

full_yr_10p_p

```{r alt-mod-fig, eval = F, fig.cap = "Another bioenergetics plot, again."}
alt_mod_p = alternative_mod %>%
  ggplot() +
  aes(x = date,
      y = cum_cons_fish_g,
      colour = temperature_c) +
  geom_line(size = 2.5) +
  scale_color_distiller(palette = "Spectral",
                        direction = -1) +
  #scale_x_date(breaks = "2 week") +
  scale_y_continuous(name = "Cumulative fish eaten (g)",
                     breaks = seq(0, 600, by = 50),
                     sec.axis = sec_axis(~. / 12,
                                         name = "Potential number of Chinook Salmon smolts",
                                         breaks = seq(0, 30, by = 2))) +
  theme_classic() +
  theme(legend.position = "top") +
  labs(color = "Temperature (C)",
       x = "Month")

alt_mod_p

@@

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()

@@

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())
